### 2020-08-03 LaTeX/sections/paper.tex
Uint testings section + results and figures

\section{Experiments}
Our application was developed in Solidity using the Truffle development framework and deployed on Ganache-CLI. We used Javascript for testing by leveraging the Mocha testing framework. Followings outline the results of different tests we performed.

@@

\textbf{\thead{Priority Queue}}    & \textbf{\thead{Maximum Number \\ of \\ Matched Orders}}      & \textbf{\thead{Cost in Gas}}      & \textbf{\thead{Cost in Gas \\ (before the \\ gas refund)}}    & \textbf{\thead{Cost in Gas\\ for \\ 1000 Pairs \\ of Orders}} \\ \hline

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 26 pairs                & 3,274,994            & 7,204,994            & 457,326,935                      \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{\thead{Heap with \\ Static Array}}           				& 28 pairs                & 3,107,527            & 7,337,527             & 333,656,805                       \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 40 pairs                & 5,414,803            & 6,644,803              & 319,481,722                       \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{Linkedlist}                       							& 90 pairs                & 3,279,847            & 7,629,847              & 35,823,601                        	\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{\thead{Linkedlist with \\ Mapping}}          				& 130 pairs              & 3,297,717            & 7,227,717               & 25,095,370                        \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %

@@

%============= Test 3 (17_Worst_Case_Submission_test.js) Figures==================== %

 \subsection{Experiments on \texttt{Submit Order()} Functions}

We executed another set of tests on the the five different versions of the CallMarket in which we sent 200 \texttt{SubmitBid} to the CallMarket to simulate two hundred of traders participating in the market. These tests were performed in two levels (i) worst case and (ii) average case submissions. 
%the data structure used for bids and asks is the same and hence the submission plots for 200 submitbids and 200 submitasks. Do we have to mention that here?

% = = = = = = = = = = = =Worst_Case_Submission = = = = = = = = = = = = =  %

\subsubsection{Worst Case Order Submission}

Here each \texttt{SubmitBid()} transaction has a price that is smallest or second-smallest of the transactions after it. Doing so, we ensure all the orders move every time a new order is sent to the market. Figure~\ref{fig:worst_case_submission} shows the gas cost variations for submitting 200 orders in five versions of the CallMarket. The x-axis is the place in line (\eg the 10th person to submit the order) and the and y-axis is the gas cost for sending that transaction.

%And conversely each \texttt{SubmitAsk()} transaction has a price that is biggest or second-biggest of the transactions after it

% = = = = = = = = = = = =Worst_Case_Submission Figure = = = = = = = = = = = = =  %

\begin{figure}[htb!p]
\centering
\includegraphics[width=1\textwidth]{fig/worst_case_submission_3.png}
\caption{\footnotesize{}  \label{fig:worst_case_submission}}
\end{figure}

% = = = = = = = = = = = =Average_Case_Submission = = = = = = = = = = = = =  %

\subsubsection{Average Case Order Submission}

Here we test the five versions of the CallMarket when 200 bid orders are entered in random ordering. To do so, we use JavaScript \texttt{Math.random()} function to generate pseudo-random integers between 1 and 100. Figure~\ref{fig:average_case_submission} shows the gas cost variations for submitting 200 orders in five versions of the CallMarket. Again the x-axis is the place in line (\eg the10th person to submit the order) and the and y-axis is the gas cost for submitting that transaction.

% = = = = = = = = = = = =Average_Case_Submission Figure = = = = = = = = = = = = =  %

\begin{figure}[htb!p]
\centering
\includegraphics[width=1\textwidth]{fig/average_case_submission_3.png}
\caption{\footnotesize{}  \label{fig:average_case_submission}}
\end{figure}

>>>>

% = = = = = = = = = = = =Uint testing the PQs Table = = = = = = = = = = = = =  %

\section{Unit Testing the Priority Queues}

Here we execute the same JavaScrip test on the five priority queues with an end goal of unit testing them. We enter 50 unsigned integers to the priority queues in random ordering. To do so, we use JavaScript \texttt{Math.random()} function to generate pseudo-random integers between 1 and 200. Figure~\ref{fig:average_uints_insertion} shows the gas cost variations for entering 50 unsigned integers in the five data structures. The x-axis is the place in line (\eg the10th number entered in the priority queue) and the and y-axis is the cost of that transaction in gas.

% = = = = = = = = = = = =average_uints_insertion Figure = = = = = = = = = = = = =  %

\begin{figure}[htb!p]
\centering
\includegraphics[width=1\textwidth]{fig/average_uints_insertion.png}
\caption{\footnotesize{}  \label{fig:average_uints_insertion}}
\end{figure}

Then, we call the \texttt{Dequeue()} function which iteratively removes the maximum value of the priority queue (until the data structure is empty). The computational costs for dequeuing 50 unsigned integers in each priority queue are outlined in Table~\ref{tab:PQ_UnitTests}. The tests are performed using the current Ethereum gas metrics (block gas limit $=$11,741,495 and 1 gas $=$ 56 gwei)~\footnote{https://ethstats.net/}. The second column of the table shows the net gas consumption (the gasUsed value derived from transaction receipts) for removing 50 integers from each priority queues.

At the time of this writing, Ethereum transaction receipts only contain the net gas consumption and not the total gas consumption ( total gas consumption is defined as $gas refunded + gasUsed$ ) and we cannot find out the value of the EVM's refund counter from inside the EVM.

So in order to account for refunds inside each priority queue smart contract, we can calculate them manually; first we figure out exactly how much storage is being cleared when dequeuing  the max integers and then we could multiply the number of storage slots cleared by 15,000 (see the last column of Table~\ref{tab:PQ_UnitTests}).

Another way to know the amount of refund in each priority queue is to use \texttt{the estimateGas API} which provides a rough idea about the total amount of gas that is required for a transaction to go through. The \texttt{web3.eth.estimateGas} pretends the transaction is included in the block  and its functions (with the parameters passed) will be executed on the Ethereum blockchain. Doing so, it provides us an estimate of how much gas is needed to be sent with the transaction. The second and third columns of Table~\ref{tab:PQ_UnitTests}) show the total amount of gas required for dequeuing 50 integers from each priority queue (provided by estimateGas) as well as the amount of gas refund ($Total Gas Consumption - gasUsed$).

Note that in order to urge miners to process smart contract with refunds, the accumulated gas refund can never exceed half the gas used up during computation~\cite{wood2014ethereum}. For example, the amount of gas that has been used when dequeuing 50 integers from the linkedlist with mapping data structure is 731,514 and since $3,000,000 > 731,514/2$, the accumulated refund through the transaction will be $731,514/2 = 365,757$.

% = = = = = = = = = = = =Uint testing the PQs Table = = = = = = = = = = = = =  %

\textbf{\thead{Priority Queue}}    & \textbf{\thead{Net Cost\\in Gas}}      & \textbf{\thead{Total Cost\\in Gas\\(from estimateGas)}}      & \textbf{\thead{Gas Refund \\(from \texttt{estimateGas})}}    & \textbf{\thead{Gas Refund \\(Manually Calculated)}} \\ \hline

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,547,031               & 3,312,378		& 765,347             & 750,000                       \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{\thead{Heap with \\ Static Array}}           				& 1,324,856                & 2,090,182     	& 765,326             & 750,000                      \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 2,863,239                & 4,378,584       	& 1,515,345           & 1,500,000                     \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{Linkedlist}                       							& 557,085               	& 1,772,085      	& 1,215,000           & 1,200,000                      \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{\thead{Linkedlist with \\ Mapping}}          				& 731,514              	& 3,731,514       	& 3,000,000     	  &  3,765,000                       \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %

\end{tabular}
\caption{\footnotesize{}
\label{tab:PQ_UnitTests}}
\end{table}
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %

%============= Experiments =================== %
\section{Experiments}

Our application was developed in Solidity using the Truffle development framework and deployed on Ganache-CLI. We used Javascript for testing by leveraging the Mocha testing framework. Followings outline the results of different tests we performed.

@@

\begin{table}[]
\centering
\begin{tabular}{|c|c|c|c|}
\hline

\textbf{\thead{Priority Queue}}    & \textbf{\thead{Maximum Number \\ of \\ Matched Orders}}      & \textbf{\thead{Net Cost\\in Gas}}          & \textbf{\thead{Net Cost in Gas\\ for \\ 1000 Pairs \\ of Orders}} \\ \hline

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 26 pairs                & 3,274,994                   	& 457,326,935                      \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{\thead{Heap with \\ Static Array}}           				& 28 pairs                & 3,107,527                  	& 333,656,805                       \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 40 pairs                & 5,414,803                     & 319,481,722                       \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{Linkedlist}                       							& 90 pairs                & 3,279,847                      & 35,823,601                        	\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{\thead{Linkedlist with \\ Mapping}}          				& 130 pairs              & 3,297,717                       & 25,095,370                        \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %

@@

%%============= Test 3 (17_Worst_Case_Submission_test.js) Figures==================== %
%
% \subsection{Experiments on \texttt{Submit Order()} Functions}
%
%We executed another set of tests on the the five different versions of the CallMarket in which we sent 200 \texttt{SubmitBid} to the CallMarket to simulate two hundred of traders participating in the market. These tests were performed in two levels (i) worst case and (ii) average case submissions. 
%%the data structure used for bids and asks is the same and hence the submission plots for 200 submitbids and 200 submitasks. Do we have to mention that here?
%
%% = = = = = = = = = = = =Worst_Case_Submission = = = = = = = = = = = = =  %
%
%\subsubsection{Worst Case Order Submission}
%
%Here each \texttt{SubmitBid()} transaction has a price that is smallest or second-smallest of the transactions after it. Doing so, we ensure all the orders move every time a new order is sent to the market. Figure~\ref{fig:worst_case_submission} shows the gas cost variations for submitting 200 orders in five versions of the CallMarket. The x-axis is the place in line (\eg the 10th person to submit the order) and the and y-axis is the gas cost for sending that transaction.
%
%%And conversely each \texttt{SubmitAsk()} transaction has a price that is biggest or second-biggest of the transactions after it
%
%% = = = = = = = = = = = =Worst_Case_Submission Figure = = = = = = = = = = = = =  %
%
%\begin{figure}[htb!p]
%\centering
%\includegraphics[width=1\textwidth]{fig/worst_case_submission_3.png}
%\caption{\footnotesize{}  \label{fig:worst_case_submission}}
%\end{figure}
%
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
%
%
%% = = = = = = = = = = = =Average_Case_Submission = = = = = = = = = = = = =  %
%
%\subsubsection{Average Case Order Submission}
%
%Here we test the five versions of the CallMarket when 200 bid orders are entered in random ordering. To do so, we use JavaScript \texttt{Math.random()} function to generate pseudo-random integers between 1 and 100. Figure~\ref{fig:average_case_submission} shows the gas cost variations for submitting 200 orders in five versions of the CallMarket. Again the x-axis is the place in line (\eg the10th person to submit the order) and the and y-axis is the gas cost for submitting that transaction. 
%
%% = = = = = = = = = = = =Average_Case_Submission Figure = = = = = = = = = = = = =  %
%
%\begin{figure}[htb!p]
%\centering
%\includegraphics[width=1\textwidth]{fig/average_case_submission_3.png}
%\caption{\footnotesize{}  \label{fig:average_case_submission}}
%\end{figure}
%
%% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
